My title

### 2024-09-18 paper/paper.qmd
add attribution

# Read data, https://stackoverflow.com/questions/78894145/quarto-document-not-seeing-project-directory-for-targets-data-functions-or-scr
raw_data <- read_csv(here("data/raw/toronto_fire_incidents.csv"))
cleaned_data <- read_csv(here("data/analysis/cleaned_fire_data_simple.csv"))
cleaned_data_tfs <-
  cleaned_data |>
  select(
    tfs_alarm_time, 
    tfs_arrival_time, 
    time_diff,
    civilian_casualties, 
    estimated_dollar_loss,
  )
cleaned_data_cat <-
  cleaned_data |>
  select(
    area_of_origin, 
    ignition_source, 
    fire_alarm_system_presence, 
    smoke_alarm_at_fire_origin, 
    sprinkler_system_operation
  )
```

@@

## Raw Data
This project uses @citeR, @opendatatoronto, @knitr, @tidyverse, @ggplot2

@@

@@

>>>>

# Read data, https://stackoverflow.com/questions/78894145/quarto-document-not-seeing-project-directory-for-targets-data-functions-or-scr
raw_data <- read_csv(here("data/raw/toronto_fire_incidents.csv"))
cleaned_data <- read_csv(here("data/analysis/cleaned_fire_data_simple.csv"))
cleaned_data_tfs <-
  cleaned_data |>
  select(
    tfs_alarm_time, 
    tfs_arrival_time, 
    time_diff,
    civilian_casualties, 
    estimated_dollar_loss,
  )
cleaned_data_cat <-
  cleaned_data |>
  select(
    area_of_origin, 
    ignition_source, 
    fire_alarm_system_presence, 
    smoke_alarm_at_fire_origin, 
    sprinkler_system_operation
  )

legend <- read.csv(here("data/legend.txt"), header = TRUE, stringsAsFactors = FALSE)
```

@@

## Raw Data
This project uses @citeR, @opendatatoronto, @knitr, @tidyverse, @ggplot2, @dplyr

@@

```{r}
#| echo: false
#| 
# Convert str to factor

cleaned_data_cat <-
  cleaned_data_cat %>%
  mutate_at(vars(
    area_of_origin,
    fire_alarm_system_presence, ignition_source,
    smoke_alarm_at_fire_origin, sprinkler_system_operation
  ), as.factor)
```

@@

\newpage

\appendix

# Appendix {#sec-appendix}

## Graph of areas of origin of fire incidents by number of occurrences {#sec-origin-fig}
```{r, fig.width=10,fig.height=11}
#| label: fig-origin
#| fig-cap: Areas of origin of fire incidents by number of occurrences
#| echo: false

cleaned_data_cat |>
  count(area_of_origin) |>
  ggplot(mapping = aes(x = n, y = area_of_origin)) +
  geom_col() + 
  theme_minimal() + 
  labs(x = "number of observation", y = "area of origin")

cat("Index of 'Area of Origin':")
cat(legend$x, sep = "\n")
```

# Attribution Statement
Contains information licensed under the Open Government Licence – Toronto. 
Visit: [https://open.toronto.ca/open-data-license/](https://open.toronto.ca/open-data-license/)
